RefactorMyCallbacks : An automation to refactor instructions from within callbacks in JavaScript\\

### 2019-05-09 latex-template/paper.tex
Update paper.tex

\title{Paper Title*\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}
\author{\IEEEauthorblockN{Ammar Tahir}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{Sheikh Abdul Mannan}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{Junaid Haroon Siddiqui}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

@@

Rest of the articles is divided into following order:
\begin{itemize}
	\item Methodology
	\item Implementation
	\item Testing
	\item Limitations and Challenges
	\item Related Work
	\item Conclusion

\end{itemize}

\section{Methodology}
Our proposed solution refactors all the independent instructions from callbacks, these can be reduced and limited to only async I/O or other blocking instruction but for simplicity we will currently refactor all independent instructions. Our solution mainly consists of 3 major parts:
\begin{itemize}
	\item AST extraction
	\item Execution context extraction
	\item Decision based refactoring
\end{itemize}
\subsection{AST extraction}
Abstract Syntax Tree is the context form of a parse tree that contains information about order of different instructions, operators and variables. An AST assigns a separate node to every operator or operand it encounters in code; thus, making a full fledge tree for the whole syntax of program. There are multiple different tools available that produce detailed AST for any given code. We can extract information like names of variables, scope of variables, structure of functions and metadata like line number in actual code etc.

@@

\begin{figure}[htbp]
	\includegraphics[scale=0.5]{code-execcon-extract.png}
	\caption{Pseudo code for Execution Context Extraction}
	\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
	\includegraphics[scale=0.5]{not-refactorable-example.png}
	\caption{An example where instruction (at line number 2) is not refactorable}
	\label{fig}
\end{figure}

\begin{figure}[htbp]
	\includegraphics[scale=0.5]{refactorable-example.png}
	\caption{An example where instruction (at line number 3) is refactorable}
	\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
	\includegraphics[scale=0.5]{code-decision-refactor.png}
	\caption{Pseudo code for Decision Based Refactoring}
	\label{fig}
\end{figure}

>>>>

\title{RefactorMyCallbacks : An automation to refactor
instructions from within callbacks in JavaScript\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}
\author{\IEEEauthorblockN{Ammar Tahir}
\IEEEauthorblockA{\textit{Computer Science Department} \\
\textit{LUMS}\\
Lahore, Pakistan \\
20100212@lums.edu.pk}
\and
\IEEEauthorblockN{Sheikh Abdul Mannan}
\IEEEauthorblockA{\textit{Computer Science Department} \\
\textit{LUMS}\\
Lahore, Pakistan \\
20100261@lums.edu.pk}
\and
\IEEEauthorblockN{Junaid Haroon Siddiqui}
\IEEEauthorblockA{\textit{Computer Science Department} \\
\textit{LUMS}\\
Lahore, Pakistan \\
junaid.siddiqui@lums.edu.pk}
}

@@

Rest of the articles is divided into following order:
\begin{enumerate}
	\item Methodology
	\item Implementation
	\item Testing
	\item Limitations and Challenges
	\item Related Work
	\item Conclusion

\end{enumerate}

\section{Methodology}
Our proposed solution refactors all the independent instructions from callbacks, these can be reduced and limited to only async I/O or other blocking instruction but for simplicity we will currently refactor all independent instructions. Our solution mainly consists of 3 major parts:
\begin{enumerate}
	\item AST extraction
	\item Execution context extraction
	\item Decision based refactoring
\end{enumerate}
\subsection{AST extraction}
Abstract Syntax Tree is the context form of a parse tree that contains information about order of different instructions, operators and variables. An AST assigns a separate node to every operator or operand it encounters in code; thus, making a full fledge tree for the whole syntax of program. There are multiple different tools available that produce detailed AST for any given code. We can extract information like names of variables, scope of variables, structure of functions and metadata like line number in actual code etc.

@@

\begin{figure}[t]
	\includegraphics[scale=0.5]{code-execcon-extract.png}
	\caption{Pseudo code for Execution Context Extraction}
	\label{fig}
\end{figure}

@@

@@

\begin{figure}[t]
	\includegraphics[scale=0.5]{not-refactorable-example.png}
	\caption{An example where instruction (at line number 2) is not refactorable}
	\label{fig}
\end{figure}

\begin{figure}[t]
	\includegraphics[scale=0.5]{refactorable-example.png}
	\caption{An example where instruction (at line number 3) is refactorable}
	\label{fig}
\end{figure}
\begin{figure}[t]
	\includegraphics[scale=0.5]{code-decision-refactor.png}
	\caption{Pseudo code for Decision Based Refactoring}
	\label{fig}
\end{figure}
